\documentclass[3p,sort&compress,11pt,fleqn,review]{elsarticle}
\bibliographystyle{elsarticle-num-names}
\usepackage{amsmath,amsfonts,amssymb,siunitx,float,subcaption,setspace,booktabs,diagbox,bm,tikz,structmech,mathtools,tikz-3dplot,pgfplots,gnuplot-lua-tikz,url,mathrsfs}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usetikzlibrary{shapes.geometric}
\pgfplotsset{compat=1.8}
\journal{}
\newcommand*{\mb}[1]{\bm{#1}}
\newcommand*{\mT}{\mathrm{T}}
\newcommand*{\md}[1]{\mathrm{d}#1}
\newcommand*{\mdd}[1]{\mathrm{d}^2#1}
\newcommand*{\eqsref}[1]{Eq.~(\ref{#1})}
\newcommand*{\figref}[1]{Fig.~\ref{#1}}
\newcommand*{\tabref}[1]{Table~\ref{#1}}
\newcommand*{\algoref}[1]{Algorithm~\ref{#1}}
\newcommand*{\secref}[1]{\S~\ref{#1}}
\newcommand*{\diag}[1]{\text{diag}\left(#1\right)}
\newcommand*{\sign}[1]{\text{sign}\left(#1\right)}
\newcommand*{\dev}[1]{\text{dev}\left(#1\right)}
\newcommand*{\tr}[1]{\text{trace}\left(#1\right)}
\newcommand*{\ddfrac}[2]{\dfrac{\md{#1}}{\md{#2}}}
\newcommand*{\pdfrac}[2]{\dfrac{\partial{#1}}{\partial{#2}}}
\newcommand{\bsigma}{\mb{\sigma}}
\newcommand{\bvarepsilon}{\mb{\varepsilon}}
\newcommand{\beeta}{\mb{\eta}}
\newcommand{\bn}{\mb{n}}
\newcommand{\balpha}{\mb{\alpha}}
\newcommand{\bbeta}{\mb{\beta}}
\newcommand{\bgamma}{\mb{\gamma}}
\newcommand{\bq}{\mb{q}}
\newcommand{\bs}{\mb{s}}
\newcommand{\bc}{\mb{c}}
\newcommand{\be}{\mb{e}}
\newcommand{\bv}{\mb{v}}
\DeclarePairedDelimiter\abs{\lvert}{\rvert}
\DeclarePairedDelimiter\norm{\lVert}{\rVert}
\makeatletter
\let\oldabs\abs
\def\abs{\@ifstar{\oldabs}{\oldabs*}}
\let\oldnorm\norm
\def\norm{\@ifstar{\oldnorm}{\oldnorm*}}
\newenvironment{breakablealgorithm}
{\begin{center}
\refstepcounter{algorithm}
\hrule height.8pt depth0pt \kern2pt
\renewcommand{\caption}[2][\relax]{
{\raggedright\textbf{\ALG@name~\thealgorithm} ##2\par}
\ifx\relax##1\relax
\addcontentsline{loa}{algorithm}{\protect\numberline{\thealgorithm}##2}
\else
\addcontentsline{loa}{algorithm}{\protect\numberline{\thealgorithm}##1}
\fi
\kern2pt\hrule\kern2pt
}}{\kern2pt\hrule\relax
\end{center}}
\begin{document}
\begin{abstract}
The time history analysis provides a convenient and efficient tool to analyse and predict the dynamic response of vibration systems. However, the corresponding numerical results are not error free. Researchers have identify various types of spurious responses. In this work, one type of spurious responses, caused by interpolation, is quantified in linear systems. It is further shown that both damping force and inertial force could be affected by the identified spurious response. The conclusion can be projected to non-linear systems with multiple degrees of freedom. To ease the issue and to improve the quality of numerical results, remedies and recommendation to the current analysis workflow are presented.
\end{abstract}
\begin{keyword}
response history analysis\sep
spurious structural response\sep
time integration\sep
digital signal processing
\end{keyword}
\begin{frontmatter}
\title{On the Causes and Remedies of Spurious Response in Dynamic Systems}
\author[add1]{Theodore~L.~Chang\corref{tlc}}\ead{tlcfem@gmail.com}
\cortext[tlc]{corresponding author}
\address[add1]{IRIS Adlershof, Humboldt-Universität zu Berlin, Berlin, Germany, 12489.}
\end{frontmatter}
\input{INTRO}
\input{THEORY}
\input{CONCLUSION}
\bibliography{BIB}
\end{document}